---
title: "GT Summary"
author: "Jack Penzer"
date: "2023-03-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(devtools)
library(roxygen2)
library(pkgdown)
library(tidyverse)
library(gt)
library(gtExtras)
library(ggplot2)
library(scales)

roxygenise(clean = TRUE)

load_all()
```

#Jack testing

## Summary table generation
```{r}
(
  summary <- topic_tec %>%
  make_gt_summary_table(group_var = name,
                        sentiment_var = sentiment)
 )
```

## Palette generation
```{r}
(
  colours <- summary %>%
  make_gt_grad_pal(positive, negative, max_colours = c("positive" = "#1b7837",
                                           "negative" = "#762a83"))
)
```



#Jamie code
```{r}
topic_tech_1 <- read_csv("~/Google Drive/My Drive/data_science_project_work/microsoft/project_work/577_joy_in_the_workplace/577_joy_in_workplace/data/tech/topics/topic_1.csv")
topic_tech_2 <- read_csv("~/Google Drive/My Drive/data_science_project_work/microsoft/project_work/577_joy_in_the_workplace/577_joy_in_workplace/data/tech/topics/topic_2.csv")
topic_tech_3 <- read_csv("~/Google Drive/My Drive/data_science_project_work/microsoft/project_work/577_joy_in_the_workplace/577_joy_in_workplace/data/tech/topics/topic_3.csv")
topic_tech_4 <- read_csv("~/Google Drive/My Drive/data_science_project_work/microsoft/project_work/577_joy_in_the_workplace/577_joy_in_workplace/data/tech/topics/topic_4.csv")
topic_tech_5 <- read_csv("~/Google Drive/My Drive/data_science_project_work/microsoft/project_work/577_joy_in_the_workplace/577_joy_in_workplace/data/tech/topics/topic_5.csv")
topic_tech <- rbind(topic_tech_1,
                    topic_tech_2,
                    topic_tech_3,
                    topic_tech_4,
                    topic_tech_5)
```

## summary - done
```{r}
```

## palettes
```{r}
min_neg <- min(topic_tech_summary$negative)
max_neg <- max(topic_tech_summary$negative)
neg_palette <- col_numeric(c("#f7f7f7", "#762a83"), domain = c(min_neg, max_neg), alpha = 0.75)
min_pos <- min(topic_tech_summary$positive)
max_pos <- max(topic_tech_summary$positive)
pos_palette <- col_numeric(c("#f7f7f7","#1b7837"), domain = c(min_pos, max_pos), alpha = 0.75)
min_user <- min(topic_tech_summary$user_satisfaction)
max_user <- max(topic_tech_summary$user_satisfaction)
user_palette <- col_numeric(c("#f7f7f7","#f7f7f7"), domain = c(min_user, max_user), alpha = 0.75)
#50E6FF
```

## gt instantiation
```{r}
tab_1 <- topic_tech_summary %>%
  janitor::clean_names() %>% 
    mutate(volume_over_time = NA,
           sent_vol_time = NA,
           sent_perc_time = NA) %>% 
  mutate(type = c("file-edit", "cart-shopping", "gamepad", 
                  "wallet", "smile"),
         .before = name) %>% 
  gt %>%
  tab_header(title = "Microsoft - 577 Joy in the workplace - Topic Modelling Summary Table") %>%
  # fmt_number(columns = positive:negative, decimals = 2) %>%
  fmt_number(columns = c(volume, 
                         # rts, 
                         # favorites
  ), sep_mark = ",", decimals = 0) %>%
  fmt_percent(columns = c(positive, negative, neutral), decimals = 1, scale_values = FALSE) %>%
  tab_source_note(source_note = "Data source: Sprinklr, Microsoft.SIP queries") %>%
  summary_rows(columns = c(volume, 
                           # rts,
                           # favorites
  ),
  fns = list(Total = "sum"),
  decimals = 0,
  missing_text = "") %>%
  data_color(columns = negative,
             colors = neg_palette) %>%
  data_color(columns = positive, colors = pos_palette) %>%
  # data_color(columns = user_satisfaction, colors = user_palette) %>%
  # opt_row_striping() %>% 
  opt_table_font(font = "Segoe UI") %>%
  gt_fa_column(column = type,
               palette = "grey",
               align = "center") %>% 
  gt_plt_bar_pct(column = user_satisfaction, scaled = TRUE,
                 fill = "#F7B500") %>% 
  tab_style(style = cell_text(weight = "600"), 
            locations = cells_title(groups = "title")) %>% 
  tab_style(style = cell_text(color = "grey50",
                              transform = "capitalize"), 
            locations = cells_column_labels(everything())) %>% 
  tab_style(style = cell_text(style = "italic"), 
            locations = cells_stub_grand_summary()) %>% 
  tab_style(style = cell_text(style = "italic"), 
            locations = cells_source_notes()) %>% 
  tab_style(style = cell_text(weight = "600"), 
            locations = cells_grand_summary()) %>% 
  tab_footnote(
    footnote = "User satisfaction = positive % + neutral %",
    locations = cells_column_labels(
      columns = user_satisfaction)) %>% 
  cols_label(type = "") %>% 
    cols_align(align = "center") %>% 
  tab_options(
    column_labels.border.top.width = px(3),
    column_labels.border.top.color = "transparent",
    #Remove border around table
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    #Adjust font sizes and alignment
    source_notes.font.size = 12,
    heading.align = "left"
    ) %>% 
    text_transform(
    locations = cells_body(columns = volume_over_time,
                           rows = name == "topic_1"),
    fn = function(x) {
      plot_1 %>%
        ggplot_image(height = px(80),
                     aspect_ratio = 2)
    }
)
# tab_1 %>% gtsave("~/Documents/gttable/tab_ggplot_1.png", expand = 20)
# tab_1 %>% gtsave("~/Documents/gttable/tab_ggplot_2.png")
# tab_1 %>% gtsave("~/Documents/gttable/tab_ggplot_3.png", expand = -10)
tab_1 %>% gtsave("~/Documents/gttable/tab_ggplot_4.png", vwidth = 2500, expand = 20)
```


# Jamie funcs
```{r}
sent_perc_fun <- function(df, topic) {
  
  df %>% 
    filter(name == topic) %>% 
    mutate(created_time_date = as.Date(created_time)) %>% 
    mutate(month = lubridate::floor_date(created_time,
                                         unit = "month")) %>% 
    group_by(month, sentiment) %>% 
    count() %>% 
    group_by(month) %>% 
    mutate(perc = n/sum(n)*100,
           sentiment = tolower(sentiment),
           month = lubridate::as_date(month)) %>% 
    ggplot(aes(x = month, y = perc, colour = sentiment)) +
    geom_line(size = 2) +
    scale_colour_manual(values = c("#762a83", "grey50", "#1b7837")) +
    scale_x_date(date_breaks = "4 month",
                 date_labels = "%b") +
    scale_y_continuous(labels = scales::label_percent(scale = 1), 
                       limits = c(0, 100),
                       breaks = c(0, 100)) + # this should be more automated
    theme(plot.title = element_blank(),
          panel.background = element_blank(),
          legend.position = "null",
          axis.title = element_blank(),
          strip.text = element_blank(),
          panel.grid = element_blank(),
          axis.text.y = element_text(size = 30),
          axis.text.x = element_text(angle = 45,
                                     size = 30,
                                     hjust = 1),
          plot.margin = margin(30, 0, 0, 0))
                       
}
```

## Map over all topics make the vol plots

###Volume plots
```{r}
splits <- topic_tech %>%
  group_split(name)

names <- sort(unique(topic_tech$name))

vol_plot_list <- map(splits, ~ .x %>%
       disp_gt_vot(date_var = created_time, time_unit = "month"))

names(vol_plot_list) <- names

vol_plot_imgs <- map(vol_plot_list, ~ .x %>% 
      gt::ggplot_image(height = px(80),
                       aspect_ratio = 2))

names(vol_plot_imgs) <- names
```

### Sentiment plots
```{r}
sent_vol_plots <- map(splits, ~.x %>%
                        disp_gt_sent_time(sentiment_var = sentiment, date_var = created_time, chart_type = "lines"), time_unit = "month")
names(sent_vol_plots) <- names
```

### add plots using the lists and an anonymous func
```{r}
gt_summary <- summary %>%
  mutate(plot_vols = " ",
         sent_plots = " ") %>%
  gt() %>%
  text_transform(locations = cells_body(
    columns = plot_vols),
    fn = function(x){
      vol_plot_list %>%
        ggplot_image(height = px(80),
                     aspect_ratio =2)
    })
```


```{r}
gt_summary <- gt_summary %>%
  text_transform(locations = cells_body(
    columns = sent_plots),
    fn = function(x){
      sent_vol_plots %>%
        ggplot_image(height = px(80),
                     aspect_ratio = 2)
    }
    )
```


# After lunch add a % option to sent function
Then make the gt programmtically with the palette fills
Investigate gt NSE/Tidy eval(?_)

```{r}
topic_tech %>%
  disp_gt_summary(sentiment_var = sentiment,
                  group_var = name,
                  date_var = date)
```

